Combined annotation exploration for SCPCP000006

### 2025-02-12 analyses/cell-type-wilms-tumor-06/notebook/07_combined_annotation_across_samples_exploration.Rmd
remove `ggpubr` dependencies and `stat_compare_mean()`

```{r packages, message=FALSE, warning=FALSE}
library(Seurat)
library(tidyverse)
library(patchwork)
library(DT)
library(ggpubr)
```

@@

  p <- ggplot(tmp, aes(x = !!sym(group.by), y = percentage, fill = !!sym(group.by))) +
  geom_boxplot()+
  scale_fill_brewer(palette="PuRd") +
  geom_dotplot(binaxis='y', stackdir='center') +
  facet_wrap(~chromosome_arm, nrow = 5 ) +
  theme_classic()  +
  stat_compare_means( method = "wilcox.test", paired = FALSE,  hide.ns = TRUE, label = "p.signif",  bracket.size = 0.5,tip.length = 0.01 ,comparison = list(comparison), size =8, label.y = 0.9)

>>>>

```{r packages, message=FALSE, warning=FALSE}
library(Seurat)
library(tidyverse)
library(patchwork)
library(DT)
```

@@

  p <- ggplot(tmp, aes(x = !!sym(group.by), y = percentage, fill = !!sym(group.by))) +
  geom_boxplot()+
  scale_fill_brewer(palette="PuRd") +
  geom_dotplot(binaxis='y', stackdir='center') +
  facet_wrap(~chromosome_arm, nrow = 5 ) +
  theme_classic()
